%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Lead Software Engineer} % Job title
    {Cere Network} % Organization
    {} % Location
    {May 2022 - present} % Date(s)
    {
      My role involves leading the development of various client-facing tools and projects. These include decentralized web applications, a web3 wallet, SDKs, and CLI tools.
      \newline
      \vspace{2mm}
      Key achievements:
      \vspace{4mm}
      \begin{cvitems}
        \item Designed and developed a multi-chain web wallet from scratch, compatible with both EVM and Substrate chains.
        \item Created a comprehensive developer toolset for our Decentralized Data Cloud protocol, including SDKs and CLI tools.
        \item Integrated the DDC protocol into various DApps, such as the NFT marketplace, Game Leaderboard, and AI recognition tool.
      \end{cvitems}
      \vspace{5mm}
      Technology stack:
      \begin{cvstackitems}
        \item TypeScript, JavaScript (ES6+)
        \item React, Redux, MobX, Storybook, Jest, React Testing Library
        \item Ethers.js, Polkadot API, Web3Auth
        \item gRPC, WebSocket
      \end{cvstackitems}
    }

  \cventry
    {Lead Frontend Engineer} % Job title
    {Evolution} % Organization
    {} % Location
    {July 2020 - May 2022} % Date(s)
    {
      As the Lead Engineer, I managed nine frontend engineers of various seniority levels spanning across three teams. I fostered positive relationships with them, aided their professional growth, and ensured their comfort within the company.
      \newline
      \vspace{2mm}
      My primary responsibilities included:
      \vspace{4mm}
      \begin{cvitems}
        \item Participating in the interview process, onboarding and mentoring new team members.
        \item Assisting individuals in setting goals and OKRs, monitoring their progress and evaluating their results.
        \item Maintaining a healthy work environment, resolving conflicts, and fostering strong relationships among teammates.
      \end{cvitems}
    }

  \cventry
    {Senior Frontend Engineer} % Job title
    {} % Organization
    {} % Location
    {Nov 2019 - May 2022} % Date(s)
    {
      \begin{cvitems} 
        \item Reorganized a complex, monolithic application by applying a micro-frontend architecture. Gradually migrated the codebase from JavaScript/CoffeeScript/AngularJS to TypeScript/React + Redux.
        \item Led the development of a cross-team UI Kit project, which is now used in all the company’s back-office applications.
        \item Designed and developed an in-house CLI tool to build, test, and release complex micro-frontend projects.
        \item Assembled, hired, and mentored a dependable team of four frontend engineers within three months.
      \end{cvitems}
      \vspace{5mm}
      Technology stack:
      \begin{cvstackitems}
        \item TypeScript, JavaScript (ES6+)
        \item React \& Redux ecosystem, Webpack, Storybook, Lerna + Yarn Workspaces, Jest, Enzyme, React Testing Library
      \end{cvstackitems}
      \vspace{-2.0mm}
    }

  \cventry
    {Senior Full Stack Engineer/Architect} % Job title
    {IOLA} % Organization
    {} % Location
    {Oct 2018 - Nov 2019} % Date(s)
    {
      \begin{cvitems}
        \item Designed, developed, and successfully released React Native iOS, Android and PWA applications.
        \item Organized Storybook driven development of UI components with visual regression testing using Jest and Puppeteer.
        \item Developed micro-frontend, platform-agnostic UI Kit based on Web Components and Preact.
        \item Developed modular GraphQL server on PHP, supporting all major GraphQL features, and full support of Relay specification.
      \end{cvitems}
      \vspace{5mm}
      Technology stack:
      \begin{cvstackitems}
        \item TypeScript, React, React Native, React Native Web, Apollo GraphQL, Babel, Webpack, Storybook, Jest, Puppeteer, Lerna
        \item PHP, SlimPHP, GraphQL-PHP, DataLoaderPHP, MySQL
      \end{cvstackitems}
      \vspace{-2.0mm}
    }

  \cventry
    {Senior Full Stack Engineer/Team Lead} % Job title
    {Klika Tech LLC} % Organization
    {} % Location
    {Oct 2016 - Sep 2018} % Date(s)
    {
      \begin{cvitems}
        \item Developed various company's projects as a full-stack JavaScript/PHP developer, including SPAs, RESTful APIs, and services.
        \item Led a team of 3 members developing JavaScript SDK utilized across all company's projects.
        \item As a team leader, was involved in interviewing, mentoring, and onboarding activities.
        \item Was the leader of the company's frontend community of more than 50 members.
      \end{cvitems}
      \vspace{5mm}
      Technology stack:
      \begin{cvstackitems}
        \item JavaScript (ES6+), React, Redux, Webpack, Babel, Mocha, Chai, Sinon
        \item PHP, PHPUnit, Pheanstalk, NodeJs, Sails, Express, MySQL
      \end{cvstackitems}
      \vspace{-2.0mm}
    }

  % \newpage

  \cventry
    {Senior Full Stack Developer/Team Lead} % Job title
    {Skalfa Asia LLC} % Organization
    {} % Location
    {Dec 2012 - Sep 2016} % Date(s)
    {
      \begin{cvitems}
        \item Led design and development of a hybrid iOS/Android application based on Ionic Framework and SlimPHP.
        \item Was a key developer in a team designing and developing open source website platforms: Oxwall, Skadate.
      \end{cvitems}
    }

  \cventry
    {Full Stack Developer} % Job title
    {} % Organization
    {} % Location
    {Jul 2010 - Dec 2012} % Date(s)
    {
      \begin{cvitems}
        \item Took part in the development and optimization of a high load SaaS solution: Wall.fm.
      \end{cvitems}
    }

  \cventry
    {Junior Full Stack Developer} % Job title
    {} % Organization
    {} % Location
    {Mar 2009 - Jul 2010} % Date(s)
    {
      \begin{cvitems}
        \item Developed various PHP/JavaScript modules for Skadate online dating platforms, including core components and add-ons.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
